Probability Distribution Checks

### 2017-07-31 01-Probability_distribution_checks.Rmd
Rename Probability check file to "01-..." to suggest order in which to run

#### Tiller Incidence Log Normal

```{r 2015_TShB_inc_norm, results='hide', message=FALSE, warning=FALSE}
AUDPS15 <- subset(AUDPS, YEAR == "2015")
f1 <- fitdist(AUDPS15$TShB_inc_AUDPS, "lnorm")
plot(f1)

car::qqp(AUDPS15$TShB_inc_AUDPS, "lnorm")
```

@@

```{r 2015_TShB_percent_norm, results='hide', message=FALSE, warning=FALSE}
AUDPS15 <- subset(AUDPS, YEAR == "2015")
f1 <- fitdist(AUDPS15$TShB_percent_AUDPS, "norm")
plot(f1)

@@

2015 Tiller AUDPS is negative, so an exponential model will not fit

@@

```{r 2015_LShB_percent_norm, results='hide', message=FALSE, warning=FALSE}
AUDPS15 <- subset(AUDPS, YEAR == "2015")
f1 <- fitdist(AUDPS15$LShB_percent_AUDPS, "norm")
plot(f1)

@@

These data do not fit this distribution, all values must be positive. There are
negative AUDPS values present.

>>>>

```{r 2015_TShB_incidence_exp, results='hide', message=FALSE, warning=FALSE}
f1 <- fitdist(AUDPS15$TShB_inc_AUDPS, "exp")
plot(f1)

car::qqp(AUDPS15$TShB_inc_AUDPS, "exp")
```

@@

```{r 2015_TShB_percent_norm, results='hide', message=FALSE, warning=FALSE}
f1 <- fitdist(AUDPS15$TShB_percent_AUDPS, "norm")
plot(f1)

@@

```{r 2015_TShB_percent_exp, results='hide', message=FALSE, warning=FALSE}
f1 <- fitdist(AUDPS15$TShB_percent_AUDPS, "exp")
plot(f1)

car::qqp(AUDPS15$TShB_percent_AUDPS, "exp")
```

@@

```{r 2015_LShB_percent_norm, results='hide', message=FALSE, warning=FALSE}
f1 <- fitdist(AUDPS15$LShB_percent_AUDPS, "norm")
plot(f1)

@@

```{r 2015_LShB_percent_exp, results='hide', message=FALSE, warning=FALSE}
f1 <- fitdist(AUDPS15$LShB_percent_AUDPS, "exp")
plot(f1)

car::qqp(AUDPS15$LShB_percent_AUDPS, "exp")
```
